Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-21 cav2017/cav2017.tex
do something about numeric representaiton section

There are two sources of error due to numeric representation; the numeric error introduced by 
the fixed point numbers used to model our plant, i.e, the plant dynamics $A_d$, $B_d$ and the states; 
and the numeric error introduced by the digital controller, which uses an analogue-to-digital converter to read
the states as a fixed-point number and performs operations in this domain. In this section we formally outline the errors introduced by
fixed point representation of numbers; in further sections we will differentiate between these
two errors by referring to them as the \emph{plant error} and the \emph{digital controller error}.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Fixed word length effects on matrix multiplications}
\label{sec:cof_fwl}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Thus far we have presented a verification procedure for a digitalized plant in a continuous space (\emph{ie} the
range of the quatizers is still $\mathbb{R}$. The next step we must reaize is that the controller 
exists in a digital program, hence its domain is $\mathbb{R}\langle I,F\rangle$. We have $\mat{A},\mat{B},\vec{x} \in \mathbb{R}^*$, $\mat{K}_d,\vec{u},\hat{\vec{x}}=\mathcal{F}\langle I,F \rangle(\vec{x}) \in \mathbb{R}\langle I,F\rangle^*$
Where $*$ represents the appropriate dimension for each matrix/vector.
Unfortunately this means that although the closed loop dynamics are in the reals, they suffer from
the fixed word restrictions in their composing elements.
Apart from the quantization errors $q_1,q_2$ there are rounding errors in the calculation of $u_k$. These will introduce a new source of quantization noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=(|\mat{K}|_1+1)c_m$

>>>>

The systems and models we consider have two sources of error due to numeric representation; the numeric error introduced by 
the fixed point numbers used to model our plant, i.e, the plant dynamics $A_d$, $B_d$ and the states; 
and the numeric error introduced by the digital controller, which uses an analogue-to-digital converter to read
the states as a fixed-point number and performs operations in this domain. In this section we formally outline the errors introduced by
fixed point representation of numbers; in further sections we will differentiate between these
two errors by referring to them as the \emph{plant error} and the \emph{digital controller error}.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Fixed word length effects on matrix multiplications}
\label{sec:cof_fwl}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\todo{this section is unclear and probably needs to move somewhere else as it is only relevant for the acceleration back end}
Thus far we have presented a verification procedure for a digitalized plant in a continuous space (\emph{ie} the
range of the quantizers is still $\mathbb{R}$. The next step we must realize is that the controller 
exists in a digital program, hence its domain is $\mathbb{R}\langle I,F\rangle$. We have $\mat{A},\mat{B},\vec{x} \in \mathbb{R}^*$, $\mat{K}_d,\vec{u},\hat{\vec{x}}=\mathcal{F}\langle I,F \rangle(\vec{x}) \in \mathbb{R}\langle I,F\rangle^*$
Where $*$ represents the appropriate dimension for each matrix/vector.
Unfortunately this means that although the closed loop dynamics are in the reals, they suffer from
the fixed word restrictions in their composing elements.
Apart from the quantization errors $q_1,q_2$ there are rounding errors in the calculation of $u_k$. These will introduce a new source of quantization noise which we may denote $\vec{\nu}_3 \in [-q_3\ \ q_3]$.
The error in $\vec{u}$ corresponds of the multiplication of $\mat{K}_d\hat{\vec{x}}$, hence $q_3=\overline{\delta}_u=(|\mat{K}|_1+1)c_m$
